\documentclass[letterpaper,11pt]{article}

% FONT: Times New Roman equivalent
\usepackage{newtxtext,newtxmath}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section Title Format
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{\vspace{-1pt}}[\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
 \item
 \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
   \small #1 & \textbf{\small #2} \\
 \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%================ RESUME START ================

\begin{document}

%----------HEADING----------
\begin{center}
{\LARGE \textbf{Sai Sindhu Bhimavarapu}}\\[4pt]
Toronto, ON \\
\href{mailto:bhimavarapusaisidhu@gmail.com}{bhimavarapusaisidhu@gmail.com} \;|\; +1 902 977 0490 \;|\;
\href{https://www.linkedin.com/in/sai-sindhu}{linkedin.com/in/sai-sindhu} \;|\;
\href{https://github.com/saisindhu}{github.com/saisindhu}
\end{center}
\vspace{-12pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.1in, label={}]
\item \small{
Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end cloud-native applications and backend services. Skilled in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with experience designing REST APIs, integrating relational/NoSQL databases, and deploying solutions on \textbf{AWS} and \textbf{Azure}. Proven experience delivering high-impact projects at \textbf{TD Bank} and \textbf{Microsoft}, with focus on performance, scalability, and backend engineering best practices.
}
\end{itemize}
\vspace{-14pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.1in, label={}]
\small{
\item \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
\item \textbf{Backend}: Spring Boot, Spring MVC, Node.js, REST APIs, Microservices \\
\item \textbf{Frontend}: React, JavaScript, HTML/CSS \\
\item \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
\item \textbf{Cloud}: AWS (EC2, Lambda, S3, CloudFormation), Azure (AKS, Data Factory), GCP \\
\item \textbf{DevOps}: Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, Terraform \\
\item \textbf{Streaming}: Apache Kafka, Event-driven architecture \\
\item \textbf{Testing}: JUnit, Cucumber, Postman, BDD/TDD \\
\item \textbf{Practices}: Agile/Scrum, System Design, Scalability, CI/CD
}
\end{itemize}
\vspace{-14pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
  {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}

\resumeSubheading
  {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
  {GRIET, Hyderabad, India}{GPA: 9.9/10}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Software Engineer}{Oct 2024 -- Present}
  {Wipro Technologies (TD Bank)}{Toronto, Canada}
\resumeItemListStart
\resumeItem{Implemented \textbf{Python} and \textbf{SQL}-based validation for fraud-detection pipelines, improving data quality and reliability.}
\resumeItem{Automated regression testing using \textbf{Java, Cucumber, Selenium}, reducing manual QA by 40\%.}
\resumeItem{Developed and maintained fraud monitoring workflows using large-scale datasets and tools like \textbf{OFSAA}.}
\resumeItem{Optimized complex SQL queries and delivered high-quality features using \textbf{Agile/Scrum}.}
\resumeItemListEnd

\resumeSubheading
  {Senior Data Engineer}{Dec 2023 -- Apr 2024}
  {LTI Mindtree (Microsoft)}{Calgary, Canada}
\resumeItemListStart
\resumeItem{Improved quality of \textbf{Azure Cognitive Services} by testing SDKs, REST APIs, and Azure AI Studio features.}
\resumeItem{Enhanced observability using \textbf{Python, Java, C\#, Kusto}, improving reliability by 30\%.}
\resumeItem{Trained and optimized \textbf{GPT models} on Azure OpenAI, improving NLP performance by 25\%.}
\resumeItem{Worked cross-functionally to validate next-gen Azure AI capabilities for enterprise applications.}
\resumeItemListEnd

\resumeSubheading
  {Software Development Engineer Co-op}{Jan 2024 -- Apr 2024}
  {ESO}{Halifax, Canada}
\resumeItemListStart
\resumeItem{Quickly mastered \textbf{XSLT, XML, C\#, C++} to deliver independent sprint work.}
\resumeItem{Contributed refactoring improvements using Pluralsight + mentorship, increasing team velocity 10–15\%.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineer}{Jan 2022 -- Aug 2022}
  {People Tech Group (General Motors)}{Hyderabad, India}
\resumeItemListStart
\resumeItem{Developed haptic feedback features for Cadillac vehicles, from concept to integration.}
\resumeItem{Built React-based UI for Cadillac design platform.}
\resumeItem{Tested haptics on prototype hardware before in-car integration.}
\resumeItem{Enhanced infotainment systems using \textbf{Qt, Rhapsody, WeCAN, C++}.}
\resumeItem{Implemented CI/CD using Jenkins and Bitbucket.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineer II}{Sep 2018 -- Jan 2022}
  {Verisk Analytics}{Hyderabad, India}
\resumeItemListStart
\resumeItem{Built analytical models using \textbf{Java, C\#, Python, C++, SQL}, improving performance 40\%.}
\resumeItem{Converted model data to binary formats using Python, reducing file sizes 90\%.}
\resumeItem{Diagnosed memory leaks + performance issues through deep debugging.}
\resumeItem{Lean Six Sigma certified; led process improvements.}
\resumeItem{Mentored new hires and served as Scrum Master for releases.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Cart Pool} | React, Node.js, Express, Jest, JWT}{Full-Stack Application}
\resumeItemListStart
\resumeItem{Built peer-to-peer delivery application with React and Node.js.}
\resumeItem{Created a responsive UI; improved engagement.}
\resumeItem{Achieved 100\% Jest coverage (TDD).}
\resumeItem{Implemented JWT authentication with SOLID design.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Expense Tracker} | AWS EC2, Lambda, DynamoDB, API Gateway}{Cloud Solution}
\resumeItemListStart
\resumeItem{Built serverless expense system using AWS stack.}
\resumeItem{Integrated Textract for receipt extraction, reducing errors 50\%.}
\resumeItem{Automated notifications with SNS + Lambda.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{PowerGrid Restoration} | Java, JUnit}{Disaster Response Simulation}
\resumeItemListStart
\resumeItem{Simulated Hurricane Fiona outage response.}
\resumeItem{Validated algorithms with JUnit.}
\resumeItem{Optimized restoration routes using data structures and algorithms.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
