\documentclass[letterpaper,10.8pt]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{mathptmx} % Times New Roman style font
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

%---------- Tighten Spacing ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\linespread{1.0}

\titlespacing*{\section}{0pt}{6pt}{3pt}
\titlespacing*{\subsection}{0pt}{4pt}{2pt}

%---------- Heading Style ----------
\titleformat{\section}{\large\bfseries}{}{}{}[{\titlerule[0.5pt]}]

%--------------- Header ---------------
\begin{document}
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\[-2pt]
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace
  \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098}
  \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--------------- Professional Summary ---------------
\section*{Professional Summary}
Results-driven Full-Stack Software Engineer with 5+ years of experience building cloud-native web applications and backend services for financial and enterprise systems. Skilled in Java/Spring Boot, Node.js/React, and Python, with strong experience designing REST APIs, integrating relational/NoSQL databases, and deploying applications on AWS and Azure. Proven track record delivering high-impact features at TD Bank, Microsoft, and other global organizations with a focus on performance, reliability, and mentoring peers in distributed systems.

%--------------- Technical Skills ---------------
\section*{Technical Skills}
\textbf{Languages:} Java, Python, C++, C\#, SQL, Bash, PowerShell \\
\textbf{Backend:} Spring Boot, Spring MVC, Node.js, REST APIs, Microservices \\
\textbf{Frontend:} React, JavaScript, HTML/CSS \\
\textbf{Databases:} PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
\textbf{Cloud:} AWS (EC2, Lambda, S3, CloudFormation), Azure (DevOps, Data Factory, AKS), GCP \\
\textbf{DevOps:} Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, Terraform, CI/CD \\
\textbf{Streaming:} Apache Kafka, Event-driven Architecture \\
\textbf{Testing:} JUnit, Cucumber, Postman, Selenium, TDD/BDD \\
\textbf{Practices:} Agile/Scrum, Code Reviews, System Design, Scalability Optimization

%--------------- Education ---------------
\section*{Education}
\textbf{Master of Applied Computer Science} \hfill Sep 2022 – Apr 2024 \\
Dalhousie University, Halifax, Canada \hfill GPA: 4.0/4.3

\textbf{Bachelor of Technology, Computer Science and Engineering} \hfill Aug 2015 – May 2019 \\
GRIET, Hyderabad, India \hfill GPA: 9.9/10

%--------------- Experience ---------------
\section*{Experience}

\textbf{Software Engineer — Wipro Technologies (TD Bank)} \hfill Oct 2024 – Present \\
Toronto, Canada
\begin{itemize}[leftmargin=10pt]
    \item Built Python and SQL validation pipelines in Azure Data Notebooks for fraud datasets, significantly improving data quality.
    \item Developed automated regression suites using Java, Selenium, and Cucumber, reducing manual testing effort by 40\%.
    \item Worked with large-scale transactional datasets and OFSAA tools to optimize fraud monitoring workflows.
    \item Designed complex SQL queries and collaborated in Agile teams to deliver multiple high-impact releases.
\end{itemize}

\textbf{Senior Data Engineer — LTI Mindtree (Microsoft)} \hfill Dec 2023 – Apr 2024 \\
Calgary, Canada
\begin{itemize}[leftmargin=10pt]
    \item Enhanced Azure Cognitive Services by testing SDKs, REST APIs, and AI workloads, improving product stability.
    \item Streamlined testing workflows using Python, Java, C\#, Kusto, Jupyter, and containers, improving observability by 30\%.
    \item Trained and optimized GPT models in Azure OpenAI, improving latency and performance by 25\%.
    \item Supported cross-functional engineering teams validating next-gen cognitive and LLM services.
\end{itemize}

\textbf{Software Development Engineer Co-op — ESO} \hfill Jan 2024 – Apr 2024 \\
Halifax, Canada
\begin{itemize}[leftmargin=10pt]
    \item Worked with XSLT, XML, C\#, and Azure to deliver sprint-ready user stories in a complex codebase.
    \item Improved code quality using refactoring and engineering best practices, increasing velocity by 10–15\%.
\end{itemize}

\textbf{Software Engineer — People Tech Group} \hfill Jan 2022 – Aug 2022 \\
Hyderabad, India
\begin{itemize}[leftmargin=10pt]
    \item Led development of haptics features for Cadillac vehicles, from requirements to integration.
    \item Built React-based design interface and integrated backend APIs for automotive configuration systems.
    \item Developed haptic testing workflows using C++, Qt, and Rhapsody for infotainment prototypes.
    \item Implemented CI/CD pipelines using Jenkins and Bitbucket, reducing deployment time.
\end{itemize}

\textbf{Software Engineer II — Verisk Analytics} \hfill Sep 2018 – Jan 2022 \\
Hyderabad, India
\begin{itemize}[leftmargin=10pt]
    \item Delivered 40\% performance improvements across several analytical models using Java, C\#, Python, C++.
    \item Built Python tools to compress model data from 2GB to 200MB, cutting loading/processing time drastically.
    \item Investigated memory leaks, optimized performance, and resolved production issues.
    \item Mentored engineers, led Scrum ceremonies, and collaborated with Product and Research teams.
\end{itemize}

%--------------- Projects ---------------
\section*{Projects}

\textbf{Cart Pool | React, Node.js, Express} \\
\begin{itemize}[leftmargin=10pt]
    \item Developed peer-to-peer delivery platform with a React interface and Node.js backend.
    \item Achieved 100\% Jest coverage and implemented secure JWT authentication.
\end{itemize}

\textbf{Expense Tracker | AWS Cloud} \\
\begin{itemize}[leftmargin=10pt]
    \item Built serverless expense tracking solution using Lambda, DynamoDB, S3, and SNS.
    \item Integrated Textract to extract data from receipts, reducing manual errors by 50\%.
\end{itemize}

\textbf{PowerGrid Restoration | Java} \\
\begin{itemize}[leftmargin=10pt]
    \item Developed algorithms for disaster recovery simulations optimizing power restoration by 35\%.
\end{itemize}

\end{document}
